FraCaS: 80 percent complete

### 2019-01-18 paper2018/paper.tex
clarification on decidability

We classify as YES if a proof can be constructed from the premises to
the hypothesis, NO if a proof of the negated hypothesis can be
constructed and UNK otherwise.\footnote{Because we work with a non-decidable logic, that poses a theoretical question that we address below.}

>>>>

We classify as YES if a proof can be constructed from the premises to
the hypothesis, NO if a proof of the negated hypothesis can be
constructed and UNK otherwise.\footnote{Because we work with a
  non-decidable logic, one can not \emph{in general} conclude
  decisively that no proof exists. Thus, we consider here that no
  proof exists if it cannot be constructed with reasonable effort. In
  particular, we test at the minimum that the automatic proof search
  built in Coq does not succeed before classifying a problem as UNK.}
